Analyzing Toronto's Dining Scene: Public Food Safety and Economic Indicators in Focus

### 2024-01-23 Outputs Folder/paper_final.qmd
Fixed typos and updated appendix

This report conducts an in-depth analysis of Dinesafe data provided by the City of Toronto's open data website OpenDataToronto [@opendatatoronto]. The author use the open-source statistical programming language R [@citeR] to display trends in the data, focusing on key indicators such as inspection pass rate and changes in infraction details. In addition, this report further examines how economic changes indicated by external factors such as the Consumer Price Index (CPI) are related to changes in public health standards within the food industry. Through analysis, results found that restaurants are more likely to violate food safety regulations, and there is a correlation between CPI fluctuations and infraction behaviours. The trend shows that the number of infraction behaviours will increase when CPI decreases.

>>>>

This report conducts an in-depth analysis of Dinesafe data provided by the City of Toronto's open data website OpenDataToronto [@opendatatoronto]. The author uses the open-source statistical programming language R [@citeR] to display trends in the data, focusing on key indicators such as inspection pass rate and changes in infraction details. In addition, this report further examines how economic changes indicated by external factors such as the Consumer Price Index (CPI) are related to changes in public health standards within the food industry. Through analysis, results found that restaurants are more likely to violate food safety regulations, and there is a correlation between CPI fluctuations and infraction behaviours. The trend shows that the number of infraction behaviours will increase when CPI decreases.
